Experience Report: Haskell in Computational Biology

### 2012-06-27 everygen.tex
an abstract that more accurately reflects the essential information in the paper

everyPt :: SearchGen pt r -> Age -> Scored pt
         -> Rand r [Aged (Utility (Scored pt))]
everyPt ss age startPt = do
  successors <- mapM (nextPt ss) (repeat startPt)
  tagged <- zipWithM agedUtility successors [succ age..]
  let (useless, Aged (Useful newPt) newAge : _) =
                        span (isUseless . unAged) tagged
  nextPts <- everyPt ss newAge newPt
  return $ Aged (Useful startPt) age : useless ++ nextPts

  where agedUtility pt age =
           utility ss move >>= \u -> return $ Aged u age
         where move = Move { older = startPt, younger = pt
                           , youngerAge = age }

>>>>

everyPt :: RandomGen r
        => SearchGen pt r -> Age -> Scored pt
        -> Rand r [Aged (Utility (Scored pt))]
everyPt sg age startPt = do
  successors <- mapM (nextPt sg) (repeat startPt)
  tagged <- zipWithM agedUtility successors [succ age..]
  let (useless, Aged (Useful newPt) newAge : _) =
                        span (isUseless . unAged) tagged
  nextPts <- everyPt sg newAge newPt
  return $ Aged (Useful startPt) age : useless ++ nextPts

  where agedUtility pt age =
           utility sg move >>= \u -> return $ Aged u age
         where move = Move { older = startPt, younger = pt
                           , youngerAge = age }

### 2012-06-27 mrfy_experience_report.tex
an abstract that more accurately reflects the essential information in the paper

\newif\iffinaldraft \finaldraftfalse % true if it's the final version

@@

%
% It can't hurt to remind everyone involved exactly what an Experience
% Report is.
%
%
\begin{abstract}
An Experience Report provides {evidence} that functional
programming really works, or it describes obstacles that prevent
functional programming from working.   
Here, we show that for computational biologists,
Haskell combines the flexibility and rapid prototyping of a scripting
language with performance comparable to~C++.
The~Haskell language and libraries provide powerful abstractions, 
but we couldn't always get them to work.
Despite some speed bumps around profiling, debugging, and the
uncertain status of any given package, we~found that Haskell's ecosystem
made it easy for us to develop new algorithms in computational
biology.
\end{abstract}

>>>>

\newif\iffinaldraft \finaldrafttrue % true if it's the final version

@@

%
% It can't hurt to remind everyone involved exactly what an Experience
% Report is.
%
%
\begin{abstract}
%An Experience Report provides {evidence} that functional
%programming really works, or it describes obstacles that prevent
%functional programming from working.   
Haskell gives computational biologists
the flexibility and rapid prototyping of a scripting
language along with performance comparable to~C++.
In~our experience, higher-order functions, lazy evaluation, and
monads really worked, but
profiling and debugging presented obstacles.
Haskell libraries varied greatly:
libraries providing memoization combinators and parallel-evaluation
strategies gave us tremendous leverage,
but other, nameless libraries mostly got in our way.
Despite the obstacles and the uncertain quality of some libraries,
Haskell's ecosystem
made it easy for us to develop new algorithms in computational
biology.
\end{abstract}
